---
output: pdf_document
---

# Homework 1, Stat 230
## Your Name


```{r setup, include=FALSE}
# Load data and packages in this setup code chunk
library(mosaic)
library(ggformula)
data("starwars", package = "dplyr")
```

## Q1.

### a. 

```{r glimpse-starwars}
# Delete this line and put your code here
```


### b. 

Pick a single numerical variable and make a histogram of it. Select a reasonable binwidth for it.

```{r histogram}
# Delete this line and put your code here
```


### c. 
Calculate summary statistics for the variable you selected in part (c) using `favstats()`.

```{r favstats}
# Delete this line and put your code here
```


### d. 
Pick a numerical variable and a categorical variable and make a visualization (you pick the type!) to visualization the relationship between the two variables. Along with your code and output, provide an interpretation of the visualization.

```{r num-cat}
# Delete this line and put your code here
```

Interpretation goes here...

### e. 
Pick a two numerical variables and make a scatterplot to visualize the relationship between the two variables. Along with your code and output, provide an interpretation of the visualization.


```{r num-num}
# Delete this line and put your code here
```

Interpretation goes here...


f. Pick a single categorical variable from the data set and make a bar plot of its distribution.

```{r cat}
# Delete this line and put your code here
```


g. Pick two categorical variables and make a visualization to visualize the relationship between the two variables. Along with your code and output, provide an interpretation of the visualization.


```{r cat-cat}
# Delete this line and put your code here
```

Interpretation goes here...
