---
title: "Homework 1"
format: pdf
due: "Friday, September 17"
---

## Due date: `r rmarkdown::metadata$due`

## Logistical details

Complete the following exercises and submit your assignment via gradescope (linked on the course webpage). To do this, take the following steps:

- Complete your assignment.
- Scan your assignment as a PDF document. 
- Upload your PDF to gradescope.
- Specify which problems are on each page.


## Problems to start after class Sept 12

#### Q1. 

The `dplyr` R package provides a `starwars` data set containing data on 87 Star Wars characters. Load the data and necessary packages using the following code chunk:

```{r message=FALSE}
library(ggformula)
library(mosaic)
data("starwars", package = "dplyr")
```

Explore the data by doing the following:

a. Use the `dplyr::glimpse()` to get an overview of the data set. 

b. Pick a single numerical variable and make a histogram of it. Select a reasonable binwidth for it. Write a sentence summarizing what you see.

(A little bit of starter code is provided below, you can use it as a starting point and fill in the blanks.)

```{r histogram, eval=FALSE}
gf_histogram(~___, data = starwars, binwidth = ___)
```

c. Calculate summary statistics for the variable you selected in part (c) using `favstats()`.

d. Pick a numerical variable and a categorical variable and make a visualization (you pick the type!) to visualization the relationship between the two variables. Along with your code and output, provide an interpretation of the visualization.

e. Pick a two numerical variables and make a scatterplot to visualize the relationship between the two variables. Along with your code and output, provide an interpretation of the visualization.

f. Pick a single categorical variable from the data set and make a bar plot of its distribution.

g. Pick two categorical variables and make a visualization to visualize the relationship between the two variables. Along with your code and output, provide an interpretation of the visualization.

