---
output: pdf_document
---

# Homework 2, Stat 230
## Your Name


```{r setup, include=FALSE}
# Load data and packages in this setup code chunk
library(mosaic)
library(ggformula)

# Load the Games2 data set
# Load the Tires data set
# Load the Hodgkins data set
# Load the Skinfold data set
```

## Q1 -- E.6


### a. 

```{r games2-eda}
# Delete this line and put your code here
```

Interpretation goes here...

### b. 

```{r games2-anova}
# Delete this line and put your code here
```

Conclusion goes here...

### c. 

```{r games2-residuals}
# Delete this line and put your code here
```

Interpretation goes here...

### d. 

Discussion goes here...

### e. 

Discussion goes here...



## Q2 --  E.9

#### a.

```{r tires-eda}
# Delete this line and put your code here
```

Interpretation goes here...


#### b.

```{r tires-anova}
# Delete this line and put your code here
```

Conclusion goes here...


#### c.

```{r tires-residuals}
# Delete this line and put your code here
```

Interpretation goes here...


#### d.

Discussion goes here...



## Q3 -- E.12

#### a.

```{r hodgkins-eda}
# Delete this line and put your code here
```

Interpretation goes here...


#### b.

```{r hodgkins-qqplot}
# Delete this line and put your code here
```

Interpretation goes here...


#### c.

```{r hodgkins-transform}
# Delete this line and put your code here
```

Interpretation goes here...


#### d.

```{r hodgkins-transform-residuals}
# Delete this line and put your code here
```

Interpretation goes here...


#### e.

```{r hodgkins-anova}
# Delete this line and put your code here
```

Conclusion goes here...


## Q4 -- E.15

#### a.

```{r skinfold-transform}
# Delete this line and put your code here
```

Results go here...


#### b.

```{r skinfold-back-transform}
# Delete this line and put your code here
```
Results and discussion goes here...
