---
title: "Homework 2"
format: pdf
due: "Friday, September 23"
---

## Due date: `r rmarkdown::metadata$due`

Complete the following exercises and submit your assignment via gradescope (linked on the course webpage). To do this, take the following steps:

## Problems to start after class Sept 16

#### Q1. 

Chapter 2 exercise E.6

You can load the `Games2` data set via 

```{r}
games2 <- read.csv("https://aloy.rbind.io/kuiper_data/Games2.csv")
```


#### Q2.

Chapter 2 exercise E.9

You can load the `Tires` data set via 

```{r}
tires <- read.csv("https://aloy.rbind.io/kuiper_data/Tires.csv")
```


## Problems to start after class Sept 19


#### Q3.

Chapter 2 exercise E.12

You can load the `Hodgkins` data set via 


```{r}
hodgkins <- read.csv("https://aloy.rbind.io/kuiper_data/Hodgkins.csv")
```


#### Q4.


Chapter 2 exercise E.15

You can load the `Skinfold` data set via 


```{r}
skinfold <- read.csv("https://aloy.rbind.io/kuiper_data/Skinfold.csv")
```

:::{.callout-tip}
In R, `log()` is the natural log (ln) and `log10()` is $\log_{10}$.
:::


<!-- ## Problems to start after class Sept 21 -->
