---
title: "Homework 5 -- Stat 230 -- Fall 2022"
format: pdf
due: "Friday, October 14"
---

## Due date: `r rmarkdown::metadata$due`

Complete the following exercises and submit your assignment via gradescope (linked on the course webpage). 



### Problems to start after class Oct 7 

#### Q1

How do bats make their way about in the dark? Echolocation requires a lot of energy. In this problem, you will explore how energy expenditure is related to body mass from 20 energy studies on three types of flying vertebrates: echolocating bats, non–echolocating bats and non–echolocating birds.


```{r}
bats <- read.csv("https://aloy.rbind.io/data/bats.csv")
```

(a) Fit a multiple linear regression model with `log(Energy)` as the response variable and `log(Mass)` and `Type` as the predictor variables. Report the fitted regression equation.

(b) What indicator variables did R create to represent the categorical variable `Type`?

(c) Based on the fitted model you reported in part (a), write a fitted model equation for each type of flying vertebrates (echolocating bats, non–echolocating bats and non–echolocating birds).

(d) Conduct the sums of squares F-test that can be used to determine whether `Type` is associated with the energy after accounting for mass. State the hypotheses, p-value, and conclusion in terms of the problem (that is, say things about the flying vertebrates).


#### Q2

Data were collected on the volume of users on the Northampton Rail Trail in Florence, Massachusetts. Variables in the data set include the number of crossings on a particular day (measured by a sensor near the intersection with Chestnut Street, `volume`), the average of the min and max temperature in degrees Fahrenheit for that day (`avgtemp`), and a dichotomous indicator of whether the day was a weekday or a weekend/holiday (`weekday`).

```{r message=FALSE, warning=FALSE}
railtrail <- read.csv("http://aloy.rbind.io/data/RailTrail.csv")
```

Consider the following full linear model predicting the volume on the Northampton Rail Trail.

```{r}
rail_lm <- lm(volume ~ hightemp + lowtemp + cloudcover + precip, data = railtrail)
```

(a) Test whether `cloudcover` can be dropped from the regression model given that `precipitation`, `hightemp`, and `lowtemp` are retained. Use an appropriate F test. State the hypotheses, p-value, and conclusion in terms of the problem (that is, say things about the rail trails and an appropriate population). [Note: you should know how to do this by hand given the ANOVA table. However, R will do the test for you with the code `anova(model1, model2)`.]


(b) Test whether both `lowtemp` and `cloudcover` can be dropped from the model given that `hightemp` and `precipitation` are retained. Use an appropriate F test. State the hypotheses, p-value, and conclusion in terms of the problem (that is, say things about the rail trails and an appropriate population).
