---
title: "Homework 7 -- Stat 230 -- Fall 2022"
format: pdf
due: "Friday, October 28"
---

## Due date: `r rmarkdown::metadata$due`

Complete the following exercises and submit your assignment via gradescope 
(linked on the course webpage). 

:::{.callout-note}
When the book asks you to "Interpret the model in terms of the odds ratio," it is asking you to interpret the slope of the logistic regression model.
:::

### Problems to start after class Oct 21 

#### Q1

The file `medschool.csv` contains data on 55 medical school applicants from a liberal arts college in the Midwest. We will focus on two variables, `Acceptance` (1 = accepted to medical school, 0 = not accepted) and `MCAT`, the student’s score on the MCAT exam.

You can load the data using the command:

```{r eval=FALSE}
medschool <- read.csv("http://aloy.rbind.io/data/medschool.csv")
```


(a) Fit the logistic regression of acceptance status on MCAT score. Report the fitted logistic regression model ($\text{logit}(\widehat{\pi}) = \cdots$).

(b) For somebody who scored 30 on the MCAT, find the probability they were accepted.

(c) For somebody who scored 30 on the MCAT, find the odds of being accepted (to not
being accepted).

(d) Compare the odds of acceptance for somebody who scored a 35 to somebody who scored a 30 on the MCAT and give a sentence interpreting this number.

(e) Interpret the coefficient of MCAT in your model (in terms of odds).


#### Q2

Chapter 7 exercise E.1

- After class on October 21, you will be able to complete part (a)
- After class on October 24, you will be able to complete parts (b)-(c)
- Skip parts (d) and (e)
- After class on October 26, you will be able to complete part (f)

Use the following code to load the data. Notice that `*` is used to denote missing values, so we add the `na.strings` argument to handle this.
```{r}
birdnest <- read.csv("https://aloy.rbind.io/kuiper_data/Birdnest.csv", na.strings = "*")
```


#### Q3

Chapter 7 exercise E.2

- After class on October 21, you will be able to complete part (a)
- After class on October 24, you will be able to complete parts (b)-(d)
- After class on October 26, you will be able to complete parts (e)-(g)

```{r}
donner <- read.csv("https://aloy.rbind.io/kuiper_data/Donner.csv")
```

For part (f) you can construct a two-way table like we did back in the EDA section. If you have {mosaic} loaded, then you can use the `tally()` command:
```{r}
#| eval: false
tally(Survived ~ Gender, data = donner)
```



### Problems to start after class Oct 24

#### Q4

Chapter 7 exercise E.5


### Problems to start after class Oct 26

#### Q5

Chapter 7 exercise E.9 parts (a)-(c)

*Hint:* You can use effects plots to display the estimated probabilities of survival in parts (a) and (b).


#### Q6

In this problem, you will look at the response residuals and measures of association to assess the two models you explore in Q5.

(a) Create a binned residual plot for where age is plotted on the x-axis for the no-interaction model from Q5 (a) and calculate the average response residual for each gender. What do the plot and group means say about the adequacy of the model? 

(b) Create a binned residual plot for where age is plotted on the x-axis for the no-interaction model from Q5 (b) and calculate the average response residual for each gender. What do the plot and group means say about the adequacy of the model? 

(c) Compare the three measures of association (Somers' D, Goodman-Kruskall gamma, and Kendall's tau-a) for the two fitted models. What do they tell you?
